Hierarchical Inference of the Intrinsic Ellipticity Distribution of Galaxies during Weak Lensing Analysis

### 2013-04-11 docs/ms.tex
Update ms.tex

>>>>

\begin{figure}

\caption{\protect\includegraphics{averagebias}\protect\includegraphics{bayesianbias}}

The upper panel shows the systematic bias of the mean ellipticity
estimator. m=$7.9\times10^{-4}\pm0.0029$ , c=$3.63\times10^{-4}\pm1.637\times10^{-4}$.The
lowwer panel shows the systembatic bias of the sample mean. m=$-0.06\pm0.00253$,
c=$3\times10^{-4}\pm1.55\times10^{-4}$ . For both cases the m,c values
are obtained from unweighted linear fit using 640,000 data points. We bin the plot into ten bins for presentation
purpose. The black square denotes the mean of $\Delta g$ in that
bin.
\end{figure}
